An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-06 Paper.tex
Change order of main and supplemental appendix
I plan to eventually have the supplemental appendix as a separate document, so
I put it after the main appendix to encourage that thought process while I write.

\section{Conclusion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window---as do Clark and West---but estimating
the benchmark model with a recursive window.  Simulations indicate
that the new statistic behaves similarly to Clark and West's original
test when the \dgp\ is stable, but can have much higher power when the
predictability varies over time, suggesting that the new statistic is
a suitable replacement in applied research.  The paper also presents a
method for comparing the benchmark model to several alternative models
simultaneously and improves block bootstrap procedures of \oos\
statistics.

\appendix
\section{Supporting Results}
This Appendix restates \citepos{Mcc:00} results, which themselves
weaken \citepos{Wes:96} assumptions, but under the dependence
conditions of Theorem~\ref{res:1}.  It also proves some of the Lemmas
required for that result and the results in the main paper.

>>>>

\section{Conclusion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window---as do Clark and West---but estimating
the benchmark model with a recursive window.  Simulations indicate
that the new statistic behaves similarly to Clark and West's original
test when the \dgp\ is stable, suggesting that the new statistic is
a suitable replacement in applied research.  The paper also presents a
method for comparing the benchmark model to several alternative models
simultaneously and improves block bootstrap procedures of \oos\
statistics.

\appendix
\section{Supporting Results}
This Appendix restates \citepos{Mcc:00} results, which themselves
weaken \citepos{Wes:96} assumptions, but under the dependence
conditions of Theorem~\ref{res:1}.  It also proves Lemmas required for
that result and the results in the main paper.
